\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-10-17 doc/USER_MANUAL/manual_SPECFEM3D.tex
adds the hdur parameter in FORCESOLUTION files and the use of a quasi-Heaviside source time function for runs involving a FORCESOLUTION file

tilted force, or an impact etc. You will need to give the East, North and vertical components of an 

@@

for the orientation of the reference frame.
This vector is made unitary internally in the code and thus only its direction matters here;

@@

The solver needs three input files in the \texttt{in\_data\_files/} directory
to run:
\begin{description}
\item [{\texttt{Par\_file}}] the main parameter file which was discussed in detail in the previous
Chapter~\ref{cha:Creating-Distributed-Databases},
\item [{\texttt{CMTSOLUTION}} or {\texttt{FORCESOLUTION}}] the earthquake source parameter file or the force source parameter file or, and
\item [{\texttt{STATIONS}}] the stations file.
\end{description}

@@

\end{figure}
{\small \par}
\end{lyxcode}
The \texttt{CMTSOLUTION} should be edited in the following way:

@@

\noindent The \texttt{FORCESOLUTION} should be edited in the following way:

\begin{itemize}
\item Set the \texttt{time shift} parameter equal to $0.0$ (the solver
will not run otherwise.) The time shift parameter would simply apply
an overall time shift to the synthetics, something that can be done
in the post-processing (see Section \ref{sec:Process-data-and-syn}).
\item Set the latitude, longitude, depth of the source in geographical
  coordinates.
\item Set the magnitude of the force source.
\item Set the components of a (non-unitary) direction vector for the
  force source in the East/North/Vertical basis (see Appendix A for
  the orientation of the reference frame).
\end{itemize}

\noindent Where  necessary, set  a \texttt{FORCESOLUTION} file  in the
same   way   you    configure   a   \texttt{CMTSOLUTION}   file   with
$N_{\mathrm{sources}}$   entries,  one   for   each  subevent   (i.e.,
concatenate  $N_{\mathrm{sources}}$ \texttt{FORCESOLUTION} files  to a
single   \texttt{FORCESOLUTION}  file).  At   least  one   entry  (not
necessarily the first) must have a  zero time shift, and all the other
entries must have non-negative time  shift. Each subevent can have its
own half latitude, longitude, depth, and force parameters.

>>>>

tilted force, or an impact etc. By default a quasi-Heaviside time function is used to represent the force point source but a Ricker 
source time function can be computed instead by changing the value of \texttt{USE\_RICKER\_IPATI} in the main constants file 
\texttt{constants.h} located in the \texttt{src/shared/} subdirectory.
Note that in the \texttt{FORCESOLUTION} file, you will need to edit the East, North and vertical components of an 

@@

for the orientation of the reference frame. This vector is made unitary internally in the code and thus only its direction matters here;

@@

The solver needs three input files in the \texttt{in\_data\_files/} directory
to run:
\begin{description}
\item [{\texttt{Par\_file}}] the main parameter file which was discussed in detail in the previous
Chapter~\ref{cha:Creating-Distributed-Databases},
\item [{\texttt{CMTSOLUTION}} or {\texttt{FORCESOLUTION}}] the earthquake source parameter file or the force source parameter file, and
\item [{\texttt{STATIONS}}] the stations file.
\end{description}

@@

\end{figure}
{\small \par}
\end{lyxcode}
The \texttt{CMTSOLUTION} file should be edited in the following way:

@@

\noindent The \texttt{FORCESOLUTION} file should be edited in the following way:

\begin{itemize}
\item Set the \texttt{time shift} parameter equal to $0.0$ (the solver
will not run otherwise.) The time shift parameter would simply apply
an overall time shift to the synthetics, something that can be done
in the post-processing (see Section \ref{sec:Process-data-and-syn}).
\item Set the \texttt{half duration} parameter of the source time function.
\item Set the latitude, longitude, depth of the source in geographical
  coordinates.
\item Set the magnitude of the force source.
\item Set the components of a (non-unitary) direction vector for the
  force source in the East/North/Vertical basis (see Appendix A for
  the orientation of the reference frame).
\end{itemize}

\noindent Where  necessary, set  a \texttt{FORCESOLUTION} file  in the
same   way   you    configure   a   \texttt{CMTSOLUTION}   file   with
$N_{\mathrm{sources}}$   entries,  one   for   each  subevent   (i.e.,
concatenate  $N_{\mathrm{sources}}$ \texttt{FORCESOLUTION} files  to a
single   \texttt{FORCESOLUTION}  file).  At   least  one   entry  (not
necessarily the first) must have a  zero \texttt{time shift}, and all the other
entries must have non-negative \texttt{time  shift}. Each subevent can have its
own half latitude, longitude, depth, \texttt{half duration} and force parameters.
